Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-25 WSSSPE1_report/WSSSPE1_summary_report.tex
Added citations that were missing

Communities are extremely important in software projects, and both
their building and continued engagement need attention during the
project life cycle.  Several of the submitted papers \todo{cite}
discussed how communities have been built around projects, and what is
needed to enable a project to grow. The latter includes public
source-code hosting, mailing lists, documentation, wikis, bug
trackers, software downloads, continuous integration, software quality
dashboards, and of course, a general web presence to tie a project's
channels and artifacts together.

@@

The papers submitted to this panel included many general
recommendations for processes, practices, tools, etc. One of the
papers \note{cite?}  suggested that a ``Software Sustainability
Institute'' should be vested with the authority to develop
standardized quality processes, a common repository, central resources
for services and consulting, a think tank of sorts, and a software
orphanage center (i.e., a place to `take care' of software when the
original developers have stopped doing so).  The idea of one common
repository received some resistance, with so many compelling
alternatives available, e.g., Bitbucket or GitHub. The centralized
communication or point of contact was seen as reasonable, with the
statement that ``vested with authority'' is perhaps too strong, but
``providing tools if needed'' might be more appropriate.

>>>>

Communities are extremely important in software projects, and both
their building and continued engagement need attention during the
project life cycle.  Several of the submitted papers
discussed how communities have been built around projects, and what is
needed to enable a project to
grow~\cite{Crusoe_WSSSPE, Hanwell_WSSSPE, Christopherson_WSSSPE, Cranston_WSSSPE, Terrel_WSSSPE}.
The latter includes public
source-code hosting, mailing lists, documentation, wikis, bug
trackers, software downloads, continuous integration, software quality
dashboards, and of course, a general web presence to tie a project's
channels and artifacts together.

@@

The papers submitted to this panel included many general
recommendations for processes, practices, tools, etc. One of the
papers suggested that a ``Software Sustainability
Institute'' should be vested with the authority to develop
standardized quality processes, a common repository, central resources
for services and consulting, a think tank of sorts, and a software
orphanage center (i.e., a place to `take care' of software when the
original developers have stopped doing so)~\cite{Crawford_WSSSPE}.
The idea of one common
repository received some resistance, with so many compelling
alternatives available, e.g., Bitbucket or GitHub. The centralized
communication or point of contact was seen as reasonable, with the
statement that ``vested with authority'' is perhaps too strong, but
``providing tools if needed'' might be more appropriate.
